Pre-registration: Patterns of interdisciplinarity in Ecology through ECOLOG
========================================================

This document acts as a pre-registration document for a project intended to highlight patterns of hiring in ecology based on publication in the ECOLOG mailing list.

The study aim to test whether:

1. The number of positions that invoke interdisciplinary, transdisciplinary or cross-disciplinary research are increasing in Ecology, as reflected by advertisments on the ECOLOG mailing list.

2. The number of interdisciplinary positions advertised is increasing faster for graduate students than it is for tenure track positions.

First: The year has multiple humps, so we are aggregating by year.  The year goes from minimum to minimum.

```{r fig.width=6}

```

Second:
Over 14 years, is the ratio of interdisciplinary grad students to tenure track positions higher than the ratio of all graduate positions to tenure track positions.

```{r}

library(ggplot2)
full.data <- data.frame(posts = rep(NA, 10000),
                        a_g   = rep(NA, 10000),
                        a_tt  = rep(NA, 10000),
                        i_g   = rep(NA, 10000),
                        i_tt  = rep(NA, 10000))

for(i in 1:10000){
  full.data[i,1] <- round(rnorm(1, 15000, 5000), 0)
  full.data[i,2] <- rbinom(1, posts, prob=0.2)
  full.data[i,3] <- rbinom(1, posts, prob=0.05)
  
  full.data[i,4] <- rbinom(1, a_g, prob=0.3)
  full.data[i,5] <- rbinom(1, a_tt, prob=0.2)
}
full.data$period <- 1:10000

ggplot(full.data, aes(x= (i_g/i_tt), y = (a_g/a_tt))) + geom_point() +
  geom_abline(intercept = 0, slope = 1)

```

Third:
Is the ratio changing over the 14 years?
```{r}
#  Use the model above, but add time term to the models, for both the number of posts, where
#  the value will be positive >1 and for the proportions, which will be beta with shifting means.
#  then just bin by year.


```
